Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-08-29 Manuscript.Rmd
Problems with LaTex integrating the images. Keep on trying (works in HTML)

library(igraph)
library(pander)
library(ggnetwork)
library(ggplot2)
library(gridExtra)
library(data.table)
library(plyr)
library(mcclust)
library(lme4)
library(parallel)
library(corrplot)
library(DescTools)

@@

Communities (i.e. clusters) were identified by means of spectral partitioning (SP; Fiedler, 1975). First, each adjusted network was represented as an $n$ x $n$ correlation matrix (where $n$ = number of vertices within the ROIs, 5,564). This matrix was then transformed into its normalized Laplacian form

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlations with every other vertex), and $A$ is the correlation matrix. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (from now on called the 'Fiedler Vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected (Fiedler, 1975). Given that this data-driven method is agnostic to the prevalent function of each community (i.e. DMN or not DMN), we defined the DMN community as the one containing the one DMN-specific area from the meta-analysis. Importantly, given the high density of these networks (**Add to results**), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016).

@@

```{r Meta-analysis ROIs, out.width="60%", out.height="40%", fig.align = "center"}
include_graphics("ROIS.png")
```

@@

```{r Template partition, out.width="60%", out.height="40%", fig.align = "center"}
include_graphics("template.png")
```

>>>>

library(igraph)
library(pander)
library(ggnetwork)
library(ggplot2)
library(gridExtra)
library(data.table)
library(plyr)
library(mcclust)
library(lme4)
library(parallel)
library(corrplot)
library(DescTools)
library(knitr)

@@

Communities (i.e. clusters) were identified by means of spectral partitioning (SP; Fiedler, 1975). First, each adjusted network was represented as an n x n correlation matrix (where n = number of vertices within the ROIs, 5,564). This matrix was then transformed into its normalized Laplacian form

@@

Where I is the identity matrix, D is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlations with every other vertex), and A is the correlation matrix. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (from now on called the 'Fiedler Vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected (Fiedler, 1975). Given that this data-driven method is agnostic to the prevalent function of each community (i.e. DMN or not DMN), we defined the DMN community as the one containing the one DMN-specific area from the meta-analysis. Importantly, given the high density of these networks (**Add to results**), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016).

@@

```{r Meta-analysis ROIs, out.width="60%", out.height="40%", fig.align = "center"}
# include_graphics("./Images/ROIS.png")
```

@@

```{r Template partition, out.width="50%", out.height="30%", fig.align = "center"}
# Load data
setwd('./Summary/')
temp <- list.files()
subjList <- sapply(temp, substring, first=1, last=6)
Summaries <- lapply(temp, read.csv)
nSubj <- length(Summaries)

#include_graphics("./Images/template.png")
```
